Collective excitations in competing phases in two and three dimensions

### 2024-01-08 paper/main.tex

In the CDW phase, both of these spectral functions become identical and form a sharp peak below the two-particle continuum.
Following the Landau theory for continuous phase transitions, this is to be expected as the free energy is expanded in terms of the order parameter as
\begin{equation}
    f(\Delta_\text{SC}) \approx r |\Delta_\text{SC}|^2 + \frac{u}{2} |\Delta_\text{SC}|^4\,,
\end{equation}
with $r > 0$ and $u > 0$ if the system is outside of the superconducting phase. \textcolor{red}{Zitieren!}
In this case, the only minimum is at $\Delta_\text{SC} = 0$. 
That means that both possible modes have to overcome the same energy to be excited at all. \textcolor{red}{Passt die Beschreibung so?}

@@

At $V=0$, both the SC and the CDW phase coexist. 
Since the degeneracy of both phases is exact \textcolor{red}{Zitat}, there should not be any difference between $\spectral{Higgs}$ and $\spectral{CDW}$ as both spectral functions capture the amplitude fluctuations of their respective order parameters.
This is precisely what can be seen in panel (b) of \autoref{fig:resolvent_overview_SC}.
Both spectral functions have a peak at $\omega = 0$ and a singularity at the lower edge of the two-particle continuum $\omega = 2\Delta_\text{tot}$, with $\Delta_\text{tot} \coloneqq \sqrt{|\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}$.

@@

$\spectral{CDW}$ shows a peak below the continuum only in the SC phase corresponding to the finite energy necessary to excite this kind of electronic density modulation.
For moderate-sized values of $V>0$, i.e., in the CDW phase, see panel (c) at $V=0.1t$, the aforementioned spectral function has a peak at $\omega=2\Delta_\text{CDW}$.
This peak becomes hard and moves outside the two-particle continuum as $V$ is increased, see panel (d) at $V=0.5t$.

$\spectral{AFM}$ is restricted to the continuum for both phases and both lattices.
For the square lattice, however, there is a peak located at the upper edge of the two-particle continuum.

>>>>

In the CDW phase, see panels (c) and (d), both of $\spectral{Higgs}$ and $\spectral{Phase}$ become identical and form a $\delta$ peak below the two-particle continuum.
Following the Landau theory for continuous phase transitions, this is to be expected as the free energy is expanded in terms of the order parameter as
\begin{equation}
    f(\Delta_\text{SC}) \approx r |\Delta_\text{SC}|^2 + \frac{u}{2} |\Delta_\text{SC}|^4\,,
\end{equation}
with $r > 0$ and $u > 0$ if the system is outside of the superconducting phase. \textcolor{red}{Zitieren!}
In this case, the only minimum is at $\Delta_\text{SC} = 0$. 
That means that both possible modes have to overcome the same energy to be excited at all. \textcolor{red}{Passt die Beschreibung so?}

@@

At $V=0$, both the SC and the CDW phase coexist. 
Since the degeneracy of both phases is exact due to the SO(4) symmetry \cite{yang90}, there should not be any difference between $\spectral{Higgs}$ and $\spectral{CDW}$ as both spectral functions capture the amplitude fluctuations of their respective order parameters.
This is precisely what can be seen in panel (b) of \autoref{fig:resolvent_overview_SC}.
Both spectral functions have a peak at $\omega = 0$ and a singularity at the lower edge of the two-particle continuum $\omega = 2\Delta_\text{tot}$, with $\Delta_\text{tot} \coloneqq \sqrt{|\Delta_\text{CDW}|^2 + |\Delta_\text{SC}|^2}$.

@@

In the SC phase, $\spectral{CDW}$ features a $\delta$ peak below the continuum corresponding to the finite energy necessary to excite this kind of electronic density modulation.
For moderate-sized values of $V>0$, i.e., in the CDW phase, see panel (c) at $V=0.1t$, the aforementioned spectral function has a singularity at $\omega=2\Delta_\text{CDW}$.
This mode becomes hard and moves outside the two-particle continuum as $V$ is increased, see panel (d) at $V=0.5t$.
\textcolor{red}{Ich muss mal suchen, ob sowas schonmal beobachtet wurde.}

$\spectral{AFM}$ is restricted to the continuum for both phases and both lattices.
For the square lattice, however, there is a singularity located at the upper edge of the two-particle continuum.
